\\Large Predicting how climate change will affect how and where terrestrial mammals will move

### 2025-06-03 writing/appendix-a-cleaning-telemetry-data.Rmd
added more info; need to expand; moving to lab pc

We start by attaching the necessary packages and sourcing some custom functions. The custom functions are all available on GitHub in the `functions` folder of the repository located at [https://github.com/QuantitativeEcologyLab/bc-mammals-temperature](https://github.com/QuantitativeEcologyLab/bc-mammals-temperature).

>>>>

\doublespacing

We start by attaching the necessary packages and sourcing some custom functions. The custom functions are all available on GitHub in the `functions` folder of the repository located at [https://github.com/QuantitativeEcologyLab/bc-mammals-temperature](https://github.com/QuantitativeEcologyLab/bc-mammals-temperature). While this appendix only shows the removal of a single outlier point, the appendix details the approach we used to clean the telemetry data. We removed outlier points using `flag_outlier(..., value = 1)`, which leverages `ctmm::as.telemetry()` to remove rows that have `TRUE` or a positive, non-zero number in the `outlier` column. See te comments in each code chunk for additional detail and considerations about individual data points.
